### 2021-04-13 input/experiments.tex
figure experiment topo
sketching experiment

\subsection{Distribution and hotspots}

\subsection{Inter-autonomous systems}

>>>>

%% \subsection{Distribution and hotspots}

% \subsection{Confirm the relevance of \NAME in the context of dynamic inter-autonomous
%   system communications.}
\subsection{Confirm that \NAME locks down the traffic of decentralized content
  indexing in the context of dynamic inter-autonomous system
  communications.}

\begin{figure}
  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}\TODO{Figure caption}}
\end{figure}

\begin{asparadesc}
\item [Description:]

We build a network by duplicating the G{\'E}ANT topology -- a real
infrastructure spanning across Europe -- and by connecting these two
clusters with a high latency link: $200$ ms simulating
cross-continental communications such as Europe-America. The
experiments comprise $2 \times 271 = 542$ \processes and we derive
intra-cluster latency from \processes' geographic location~\REF.

\noindent We evaluate the traffic of \NAME by measuring the average
number of messages per \process over the experiments. In the first
experiment, at $50$ ms, only one process becomes source, hence there
is only one partition for the whole distributed system. In the second
experiment, at $50$ ms, two processes become sources, one per
cluster. Afterwards both scenarios are identical. At $500$ ms, we
remove the link between the two clusters. At $1200$ ms, we insert this
link again.

Figure~\ref{fig:geant} shows the results of this experimentation. The
top part corresponds to the one source experiment, while the bottom
part corresponds to the one source per cluster experiment.

\noindent Figure~\ref{fig:geant} confirms that concurrent \texttt{Add}
may generate additional traffic, for processes may deliver and forward
a partition only to later realize that they have a closer source.

\noindent Figure~\ref{fig:geant} highlights that removing the
inter-continental link generates additional traffic. The cluster cut
off the source must remove control information about this
source. \TODO{There are both $\alpha$s and $\delta$s.}  \TODO{The
  protocol works when physical partitions exist. The cluster with the
  source belong to the same partition. The other cluster does not
  belong to any partition.}

\noindent Figure~\ref{fig:geant} shows that, when adding the link
again, the two clusters communicate again. \TODO{More.}

\noindent Finally, Figure~\ref{fig:geant} \TODO{(overall less
  traffic)} empirically demonstrates that \NAME favor
replication. \TODO{More.}
\end{asparadesc}
